Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-01-25 paper.tex
adding SOM figures
adding contents provided by Hossam

\subsubsection{Experimental setup}

@@

\subsubsection{Obtained results}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.60]{freq-sales}
\end{center}
\caption{Number of books in each category.}
\label{fig:count}
\end{figure*}

@@

In Figure \ref{fig:Umatrix} we label the U-matrix with the Total Sales categories. It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions. In the top of the U-matrix the VL category is located. The L category appears in the middle of the matrix. Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner. 
Inspecting the component \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components have the highest similarity to the clusters shown in the U-matrix. Based on this analysis, those features will be selected for the next stage.

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.80]{fig1}
\end{center}
\caption{U-matrix and component planes.}
\label{fig:componentplanes}
\end{figure*}

\begin{figure*}[http]
\centering
    \begin{subfigure}[b]{0.32\textwidth}            
            \includegraphics[scale=0.50]{Umatrix.eps}
            \caption{U-matrix}
            \label{fig:Um}
    \end{subfigure}%
    \begin{subfigure}[b]{0.32\textwidth}  
            \includegraphics[scale=0.50]{Labels.eps}
            \caption{Labels}
            \label{L}
    \end{subfigure}

    \caption{Labeling the U-matrix using the Total Sales variable.}
\label{fig:Umatrix}
\end{figure*}

@@

\begin{figure*}[http]
\centering
    \begin{subfigure}[b]{0.32\textwidth}            
            \includegraphics[scale=0.32]{m5p.eps}
            \caption{M5P}
            \label{fig:M5P}
    \end{subfigure}%
    \begin{subfigure}[b]{0.32\textwidth}  
            \includegraphics[scale=0.32]{lr.eps}
            \caption{LR}
            \label{fig:LR}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{svm.eps}
            \caption{SVM}
            \label{SVM}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{knn.eps}
            \caption{k-NN}
            \label{fig:k-NN}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{mlp.eps}
            \caption{MLP}
            \label{MLP}
    \end{subfigure}
    \caption{Actual VS predicted sales for M5P, LR, SVM, k-NN, MLP models.}
\label{conv2}
\end{figure*}

\begin{figure*}[http]
\centering
    \begin{subfigure}[b]{0.32\textwidth}            
            \includegraphics[scale=0.32]{m5p_RAE.eps}
            \caption{M5P}
            \label{fig:M5P1}
    \end{subfigure}%
    \begin{subfigure}[b]{0.32\textwidth}  
            \includegraphics[scale=0.32]{lr_RAE.eps}
            \caption{LR}
            \label{fig:LR1}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{svm_RAE.eps}
            \caption{SVM}
            \label{SVM1}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{knn_RAE.eps}
            \caption{k-NN}
            \label{fig:k-NN1}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{mlp_RAE.eps}
            \caption{MLP}
            \label{MLP1}
    \end{subfigure}
    \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
\label{conv2ReliefAttributeEval}
\end{figure*}

\begin{figure*}[http]
\centering
    \begin{subfigure}[b]{0.32\textwidth}            
            \includegraphics[scale=0.32]{m5p_CFS.eps}
            \caption{M5P}
            \label{fig:M5P2}
    \end{subfigure}%
    \begin{subfigure}[b]{0.32\textwidth}  
            \includegraphics[scale=0.32]{lr_CFS.eps}
            \caption{LR}
            \label{fig:LR2}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{svm_CFS.eps}
            \caption{SVM}
            \label{SVM2}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{knn_CFS.eps}
            \caption{k-NN}
            \label{fig:k-NN2}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{mlp_CFS.eps}
            \caption{MLP}
            \label{MLP2}
    \end{subfigure}
    \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
\label{conv2CfsSubsetEval}
\end{figure*}

\begin{figure*}[http]
\centering
    \begin{subfigure}[b]{0.32\textwidth}            
            \includegraphics[scale=0.32]{m5p_SOM.eps}
            \caption{M5P}
            \label{fig:M5P2}
    \end{subfigure}%
    \begin{subfigure}[b]{0.32\textwidth}  
            \includegraphics[scale=0.32]{lr_SOM.eps}
            \caption{LR}
            \label{fig:LR2}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{svm_SOM.eps}
            \caption{SVM}
            \label{SVM2}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{knn_SOM.eps}
            \caption{k-NN}
            \label{fig:k-NN2}
    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
            \includegraphics[scale=0.32]{mlp_SOM.eps}
            \caption{MLP}
            \label{MLP2}
    \end{subfigure}
    \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
\label{conv2SOM}
\end{figure*}

>>>>

\subsection{Experimental setup}

@@

\subsection{Obtained results}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.60]{freq_sales.eps}
\end{center}
\caption{Number of books in each category.}
\label{fig:count}
\end{figure*}

@@

In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales categories. It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions. In the top of the U-matrix the VL category is located. The L category appears in the middle of the matrix. Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner. 
Inspecting the component \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components have the highest similarity to the clusters shown in the U-matrix. Based on this analysis, those features will be selected for the next stage.

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{SOM_figure.eps}
\end{center}
\caption{U-matrix and component planes.}
\label{fig:componentplanes}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{cc}
\includegraphics[scale=0.55]{Umatrix.eps}  &
\includegraphics[scale=0.55]{Labels.eps}  \\
U-matrix & Labels 
\end{tabular}
\end{center} 
\caption{Labeling the U-matrix using the total-sales variable.}
\label{fig:Umatrix} 
\end{figure*}

@@

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p.eps}  &
\includegraphics[scale=0.22]{lr.eps}   &
\includegraphics[scale=0.22]{svm.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn.eps}  &
\includegraphics[scale=0.22]{mlp.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sales for M5P, LR, SVM, k-NN, MLP models.}
\label{conv2}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p_RAE.eps}  &
\includegraphics[scale=0.22]{lr_RAE.eps}   &
\includegraphics[scale=0.22]{svm_RAE.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn_RAE.eps}  &
\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
\label{conv2ReliefAttributeEval}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p_CFS.eps}  &
\includegraphics[scale=0.22]{lr_CFS.eps}   &
\includegraphics[scale=0.22]{svm_CFS.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn_CFS.eps}  &
\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
\label{conv2CfsSubsetEval}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p_SOM.eps}  &
\includegraphics[scale=0.22]{lr_SOM.eps}   &
\includegraphics[scale=0.22]{svm_SOM.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn_SOM.eps}  &
\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
\label{conv2SOM}
\end{figure*}
